---
title: "Natural Gas Dashboard – April 22, 2025"
format:
  dashboard:
    orientation: rows
    logo: images/gadex_logo.png
---

```{r}
#| echo: false
#| results: hide
library(pacman)

# Use pacman to load and install the required packages
pacman::p_load(
  dplyr,
  flextable,
  forecast,
  ggplot2,
  ggsci,
  ggthemes,
  gt,# For data visualization
  kableExtra,
  leaflet,
  lubridate,
  purrr,
  pdftools,
  plotly,
  Polychrome,
  readr, # For reading and writing data
  readxl,
  reactable,
  sf,
  shiny,
  stringr,
  tidyverse,
  tidyr,
  writexl,
  xts
  )
```

```{r}
#| echo: false
#| results: hide
source("theme_bloom.R")
```

```{r}
#| echo: false
#| results: hide
base_colors <- c("black","dodgerblue","gray30","turquoise","gray65","seagreen3")
```

```{r}
#| echo: false
#| results: hide
sched_by_type <- readRDS("inputs/sched_by_type.rds")
sched_effe <- readRDS("inputs/qt11_05_sched_effe.rds")
leaflet_map <- readRDS("inputs/qt11_07_leaflet_map.rds")
```

# Intro

##  {.sidebar}

## Overview {width="40%"}

```{r}
#| title: Sistrangas receipt locations
```

##  {width="60%"}

###  {height="50%"}

```{r}
#| title: Sistrangas receipt locations
leaflet_map
```

###  {height="50%"}

```{r}
#| title: Sistrangas receipt locations
#| fig-width: 5
#| fig-asp: 0.7

reactable(sched_effe)
```

# SISTRANGAS Glimpse

##  {.sidebar}

**Scheduled Flows**

**Pre-arranged quantities** of natural gas scheduled to flow through pipeline locations during a **commercial gas day**.

Each tab displays a combination of nodes, reflecting different supply sources:

• **Domestic**: originating from processing plants and production fields

• **Imported**: delivered via direct cross-border interconnections or through other pipelines developed within Mexico.

Plots prepared by GADEX using information from CENAGAS.





There is an interactive dashboard available to GADEX and ENIX patrons.

Contact: eduardo.prudhomme\@gadex.mx

```{r}
#| echo: false
#| results: hide
plot_key_loc <- readRDS("inputs/qt11_04_plot_key_loc.rds")
plot_makeups <- readRDS("inputs/qt11_04_plot_makeups.rds")

plot_smp <- readRDS("inputs/qt11_05_plot_smp.rds")
plot_typesp <- readRDS("inputs/qt11_05_plot_typesp.rds")
sched_tdy_smp <- readRDS("inputs/qt11_05_sched_tdy_smp.rds")
sched_by_type <- readRDS("inputs/qt11_05_sched_by_type.rds")

```

##  {.tabset}

### Selected nodes

#### 

```{r}
#| title: Today's selection
sched_tdy_smp
```

```{r}
#| title: Makeups
plot_makeups
```

#### 

```{r}
#| title: Day by day
plot_key_loc
```

```{r}
#| title: Average by month
plot_smp
```

### Selected source

####

```{r}
#| title: Today's selection
sched_by_type[["border"]]
```


#### 

```{r}
#| title: Today's selection
plot_typesp
```

### Tafiff Zones

#### 

```{r}
#| title: Today's selection
plots_zonesp <- readRDS("inputs/qt11_06_plots_zonesp.rds")

plots_zonesp
```


#### 

```{r}
#| title: Today's selection
sched_by_zone_plot <- readRDS("inputs/qt11_06_sched_by_zone_plot.rds")

sched_by_zone_plot
```

```{r}
#| title: Today's selection
sched_by_zone_stacked_plot <- readRDS("inputs/qt11_06_sched_by_zone_stacked_plot.rds")

sched_by_zone_stacked_plot
```



### Tab 4

#### 



#### 



# Sistrangas {orientation="rows"}

## Sections {.tabset}

### General {orientation="columns"}

####  {width="30%"}


####  {width="30%"}


### Processing plants {orientation="rows"}

####  {width="30%"}


####  {width="30%"}

```{r}
plots_by_type <- readRDS("files_talks/talk_01/inputs/plots_by_type.rds")

plots_by_type[["Processing plant"]]
```

```{r}
sched_by_type[["Processing plant"]]

```

####  {width="40%"}

```{r}
#| title: Processing plant cycles


```

### Cycles

### Info {orientation="columns"}

```{r}
#| title: Sistrangas receipt locations
#| fig-width: 5
#| fig-asp: 0.7
nodes_rec_tab <- readRDS("inputs/qt11_01_nodes_rec_tab.rds")

reactable(nodes_rec_tab)
```


# Scheduled Flows

##  {.sidebar}

**Scheduled Flows**

**Pre-arranged quantities** of natural gas scheduled to flow through pipeline locations during a **commercial gas day**.

Each tab displays a combination of nodes, reflecting different supply sources:

• **Domestic**: originating from processing plants and production fields

• **Imported**: delivered via direct cross-border interconnections or through other pipelines developed within Mexico.

Plots prepared by GADEX using information from CENAGAS.





There is an interactive dashboard available to GADEX and ENIX patrons.

Contact: eduardo.prudhomme\@gadex.mx

```{r}
#| echo: false
#| results: hide
plots_sched <- readRDS("inputs/in01/qt11_03_plots_sched.rds")

```

##  {.tabset}

### Tab 1

#### 

```{r}
#| title: V025 Cactus
ply01 <- make_plotly_A(plots_sched[["V025"]])

ply01
```

```{r}
#| title: V045 Mendoza
ply02 <- make_plotly_A(plots_sched[["V045"]])

ply02
```

#### 

```{r}
#| title: V061 Ramones
ply03 <- make_plotly_A(plots_sched[["V061"]])
ply03
```

```{r}
#| title: V076 Gaza (Gasoducto Zapotlanejo)
ply04 <- make_plotly_A(plots_sched[["V076"]])
ply04
```

### Tab 2

#### 

```{r}
#| title: V9B6 Burgos
ply01 <- make_plotly_A(plots_sched[["V9B6"]])

ply01
```

```{r}
#| title: V042 Playuela
ply02 <- make_plotly_A(plots_sched[["V042"]])

ply02
```

#### 

```{r}
#| title: V032 Kinder Morgan Border
ply03 <- make_plotly_A(plots_sched[["V032"]])
ply03
```

```{r}
#| title: V062 El Sauz
ply04 <- make_plotly_A(plots_sched[["V062"]])
ply04
```

### Tab 3

#### 

```{r}
#| title: V907 La Venta
ply01 <- make_plotly_A(plots_sched[["V907"]])

ply01
```

```{r}
#| title: V056 Campo Nejo
ply02 <- make_plotly_A(plots_sched[["V056"]])

ply02
```

#### 

```{r}
#| title: V067 Energy Transfer
ply03 <- make_plotly_A(plots_sched[["V067"]])
ply03
```

```{r}
#| title: V030 Gloria a Dios
ply04 <- make_plotly_A(plots_sched[["V030"]])
ply04
```

### Tab 4

#### 

```{r}
#| title: V908 Matapionche
ply01 <- make_plotly_A(plots_sched[["V908"]])

ply01
```

```{r}
#| title: V036 Monclova
ply02 <- make_plotly_A(plots_sched[["V036"]])

ply02
```

#### 

```{r}
#| title: V033 Tennessee
ply03 <- make_plotly_A(plots_sched[["V033"]])
ply03
```

```{r}
#| title: V074 Montegrande
ply04 <- make_plotly_A(plots_sched[["V074"]])
ply04
```



# Nomination Cycles

##  {.sidebar}

**Nomination Cycles**

**Nominated** volumes of natural gas submitted during each phase of the commercial gas day cycle, organized by pipeline location..

Each tab displays nodes according the tariff zone they belong

Plots prepared by GADEX using information from CENAGAS.





There is an interactive dashboard available to GADEX and ENIX patrons.

Contact: eduardo.prudhomme\@gadex.mx

##  {.tabset}

### Zone 1 / Zone 3

#### 

```{r}
#| title: Z1- Gloria a Dios
plots_nomina <- readRDS("inputs/qt11_02_plots_nomina.rds")

plyV030 <- make_plotly_B(plots_nomina[["V030"]])
plyV030
```

```{r}
#| title: Z1- Leon Guzman 
plyV078 <- make_plotly_B(plots_nomina[["V078"]])
plyV078
```

#### 

```{r}
#| title: Z3- Kinder Morgan MTY 
plyV037 <- make_plotly_B(plots_nomina[["V037"]])
plyV037
```

```{r}
#| title: Z3- Ramones Fase 1 
plyV061 <- make_plotly_B(plots_nomina[["V061"]])
plyV061
```

### Zone 3

#### 

```{r}
#| title: Kinder Morgan Border 
plyV032 <- make_plotly_B(plots_nomina[["V032"]])
plyV032
```

```{r}
#| title: Energy Transfer
plyV067 <- make_plotly_B(plots_nomina[["V067"]])
plyV067
```

#### 

```{r}
#| title: Tennessee
plyV033 <- make_plotly_B(plots_nomina[["V033"]])
plyV033
```

```{r}
#| title: TETCO
plyV034 <- make_plotly_B(plots_nomina[["V034"]])
plyV034
```

### Zone 3 / Zone 4

#### 

```{r}
#| title: Z3- Monclova
plyV036 <- make_plotly_B(plots_nomina[["V036"]])
plyV036
```

```{r}
#| title: Z3- Burgos
plyV9B6 <- make_plotly_B(plots_nomina[["V9B6"]])
plyV9B6
```

#### 

```{r}
#| title: Z4- Campo Nejo
plyV056 <- make_plotly_B(plots_nomina[["V056"]])
plyV056
```

```{r}
#| title: Z4- Mareografo
plyV059 <- make_plotly_B(plots_nomina[["V059"]])
plyV059
```

### Zone 5

#### 

```{r}
#| title: El Sauz
plyV062 <- make_plotly_B(plots_nomina[["V062"]])
plyV062
```

```{r}
#| title: Montegrande 
plyV074 <- make_plotly_B(plots_nomina[["V074"]])
plyV074
```

#### 

```{r}
#| title: CPG Poza Rica 
plyV905 <- make_plotly_B(plots_nomina[["V905"]])
plyV905
```

```{r}
#| title: Raudal 
plyV051 <- make_plotly_B(plots_nomina[["V051"]])
plyV051
```

### Zone 6 / Zone 7

####

```{r}
#| title: Z6- El Castillo
plyV918 <- make_plotly_B(plots_nomina[["V918"]])
plyV918
```

```{r}
#| title: Z6- Gasoducto Zapotlanejo 
plyV076 <- make_plotly_B(plots_nomina[["V076"]])
plyV076
```

####

```{r}
#| title: Z7- PEP Mendoza
plyV045 <- make_plotly_B(plots_nomina[["V045"]])
plyV045
```

```{r}
#| title: Z7- Playuela 
plyV042 <- make_plotly_B(plots_nomina[["V042"]])
plyV042
```

### Zone 7 / Zone 8

####

```{r}
#| title: Z7- Matapionche
plyV908 <- make_plotly_B(plots_nomina[["V908"]])
plyV908
```

```{r}
#| title: Z8- La Venta
plyV042 <- make_plotly_B(plots_nomina[["V042"]])
plyV042
```

####

```{r}
#| title: Z8- Cactus - Nuevo Pemex
plyV025 <- make_plotly_B(plots_nomina[["V025"]])
plyV025
```


# prices {orientation="rows"}

## Value boxes {height="25%"}

```{r}
#| label: calculate-values
lowest_mileage_cty <- mpg |>
filter(cty == min(cty)) |>
distinct(cty) |>
pull(cty)

highest_mileage_cty <- mpg |>
filter (cty == max(cty)) |>
distinct(cty) |>
pull (cty)

rounded_mean_city_mileage <- mpg |>
  summarize(round(mean(cty), 2)) |>
  pull()
```

```{r}
#| content: valuebox
#| title: "Least efficient"
#| icon: fuel-pump-fill
#| color: danger
list(
value = paste(lowest_mileage_cty, "mpg")
)

```

```{r}
#| content: valuebox
#| title: "Most efficient"
#| icon: fuel-pump
#| color: success
list(
value = paste(highest_mileage_cty, "mpg")
)

```

## El Encino
